Paper 1 Analysis

### 2015-10-22 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
New version of alphas graph.

<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=1.5, fig.cap="Historical cost shares for capital and labor.">>=
ggplot(data = gather(CostShares, key=cost_share, value=value, cs_k, cs_l)) + 
  geom_line(mapping = aes(
    x = Year, 
    y = value, 
    group = cost_share, 
    linetype = cost_share,
    color = cost_share,
    size = cost_share)) +
  facet_grid( ~ Country) +
  ylab("Cost Share") +
  scale_y_continuous(limits=c(-0.2, 1.1), breaks=c(0, 0.5, 1)) +
  geom_hline(aes(yintercept = 0.3), colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = 0.7), colour="gray50", size=0.1) +
  xlab("") +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_color_manual(name = "", 
                     labels=c("k", "l"),
                     values=c("black", "black")) +
  scale_linetype_manual(name="", 
                        labels=c("k", "l"),
                        values=c(2,3)) + 
  scale_size_manual(name="", 
                    labels=c("k", "l"),
                    values = c(0.9, 0.9)) +
  xy_theme()
@

@@

<<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=
AllOE %>% 
  mutate(split =
           as.character(
             interaction(
               factor(flavor, labels = c("QA", "UA")), 
               factor(nest, 
                      labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
               sep = ", ",
               lex.order = FALSE ) )
  ) %>%
  gather(factor, elasticity, oe1, oe2, oe3) %>%
  mutate(
    split2 = relevelFactor(
      factor(split), 
      paste( rep(c("UA", "QA"), times = 4 ), 
             rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
             sep=", ")
    )
  ) %>%
  ggplot(aes(x=Year)) + 
  geom_line( 
    alpha = .8, # size=1.0,
    aes(y = elasticity, 
        colour = factor,
        linetype=factor,
        size = factor
    ) ) +
  facet_grid(split2 ~ Country) +
  scale_color_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c("black", "black", "gray70")
  ) +
  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
  scale_y_continuous(breaks = c(0.0, 0.5, 1.0), limits=c(-0.2, 1.2)) +
  scale_size_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values = c(.9, .9, .6)) +
  scale_linetype_manual( 
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c(2,3,1) ) + 
  labs(x="", y="") +
  xy_theme()
@

>>>>

<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=1.5, fig.cap="Historical cost shares for capital and labor.", eval=FALSE>>=
ggplot(data = gather(CostShares, key=cost_share, value=value, cs_k, cs_l)) + 
  geom_line(mapping = aes(
    x = Year, 
    y = value, 
    group = cost_share, 
    linetype = cost_share,
    color = cost_share,
    size = cost_share)) +
  facet_grid( ~ Country) +
  ylab("Cost Share") +
  scale_y_continuous(limits=c(-0.2, 1.1), breaks=c(0, 0.5, 1)) +
  geom_hline(aes(yintercept = 0.3), colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = 0.7), colour="gray50", size=0.1) +
  xlab("") +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_color_manual(name = "", 
                     labels=c("k", "l"),
                     values=c("black", "black")) +
  scale_linetype_manual(name="", 
                        labels=c("k", "l"),
                        values=c(2,3)) + 
  scale_size_manual(name="", 
                    labels=c("k", "l"),
                    values = c(0.9, 0.9)) +
  xy_theme()
@

@@

<<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=
AllOE %>% 
  mutate(
    xfacet = as.character(
                interaction(Country, factor(flavor, labels = c("QA", "UA")), sep = " - ")
    ),
    yfacet = as.character(
                interaction(factor(nest, labels = c("(ek)l", "kl", "(kl)e", "(le)k")), CSP, sep = " - ")
    )
  ) %>% 
  gather(key = oe_type, value = oe_value, oe1, oe2, oe3) %>%

  ggplot(aes(x = Year)) +
  geom_line(alpha = 0.8, aes(y = oe_value, 
            color = oe_type,
            linetype = oe_type,
            size = oe_type)) + 
  facet_grid(yfacet ~ xfacet) + 
  scale_color_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c("black", "black", "gray70")
  ) +
  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
  scale_y_continuous(breaks = c(0.0, 0.5, 1.0), limits=c(-0.2, 1.2)) +
  scale_size_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values = c(.9, .9, .6)) +
  scale_linetype_manual( 
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c(2,3,1) ) + 
  labs(x="", y="") +
  xy_theme()

# AllOE %>% 
#   mutate(split =
#            as.character(
#              interaction(
#                factor(flavor, labels = c("QA", "UA")), 
#                factor(nest, 
#                       labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
#                sep = ", ",
#                lex.order = FALSE ) )
#   ) %>%
#   gather(factor, elasticity, oe1, oe2, oe3) %>%
#   mutate(
#     split2 = relevelFactor(
#       factor(split), 
#       paste( rep(c("UA", "QA"), times = 4 ), 
#              rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
#              sep=", ")
#     )
#   ) %>%
#
#   ggplot(aes(x=Year)) + 
#   geom_line( 
#     alpha = .8, # size=1.0,
#     aes(y = elasticity, 
#         colour = factor,
#         linetype=factor,
#         size = factor
#     ) ) +
#   facet_grid(split2 ~ Country) +
#   scale_color_manual(
#     name = "",
#     labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
#     values=c("black", "black", "gray70")
#   ) +
#   scale_x_continuous(breaks = c(1960, 1980, 2000)) +
#   scale_y_continuous(breaks = c(0.0, 0.5, 1.0), limits=c(-0.2, 1.2)) +
#   scale_size_manual(
#     name = "",
#     labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
#     values = c(.9, .9, .6)) +
#   scale_linetype_manual( 
#     name = "",
#     labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
#     values=c(2,3,1) ) + 
#   labs(x="", y="") +
#   xy_theme()
